miniKanren with fair search strategies

### 2019-05-21 Paper/paper.tex
deadline
change disj macro folloing the suggestion by Dan

%%% NOTE %%%
%
%  SUBMISSION DEADLINE: May 15, 2019
%
%%%%%%%%%%%%

@@

@@

\begin{figure}
	\lstinputlisting{Figures/DFSi.rkt}
	\caption{implementation of \DFSi}
	\label{DFSi}
\end{figure}

Fig.~\ref{DFSi} shows parts that are later compared with other search 
strategies. We follow some conventions to name variables: variables bound to 
states are named \texttt{s}; variables bound to goals are named \texttt{g} 
(possibly with subscript); variables bound to search spaces have names ending 
with $^\infty$. The first function, \texttt{disj2}, implements binary 
disjunction. if and only if is its helper, which composes two disjunctive 
search spaces. The following function, \texttt{conj2}, implements binary 
conjunction. 
It applies the \emph{first} goal to the input state, then applies the second 
goal to states in the resulting search space. The latter process is done with a 
helper function. \texttt{append-map$^\infty$} applies its input goal to states 
in its input search spaces and compose the resulting search spaces. It reuses 
\texttt{append$^\infty$} for search space composition. The following and last 
two definitions say disjunctive operator and conjunctive operator are 
right-associative.

@@

Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
\conj{}. The implementation of DFS$_\textrm{bi}$ differs from 
DFS$_\textrm{i}$'s in the \disj{} macro. We list the new \disj{} with its 
helper in Fig.~\ref{balanced-disj}. When there are one or more disjunctive 
goals, \disj{} builds a balanced binary tree whose leaves are the goals and 
whose nodes are \texttt{disj2}s, hence the name of this search strategy. 
The first ``argument'' to \texttt{disj+} is the goals. And the next two 
``arguments'' accumulate goals to be put in the left and right subtrees. When 
there is only one goal, the tree is the goal itself. This case is handled in 
the first clause. When there are more goals, we partition the list of goals 
into two sublists of roughly equal lengths and recur on the two sublists. The 
partition is done by repetitively dispatching the first two goals in the list 
to the accumulators, until only 
zero or one goal remains. The two base cases of the partition are handled by 
the second and the third clauses respectively. And the dispatching is done at 
the fourth and last clause. In contrast, the \disj{} in \DFSi{} constructs the 
binary tree in a particularly unbalanced form.

% The first helper function, \texttt{split}, takes a 
% list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} 
% into two sub-lists of roughly equal length, and returns the application of 
% \texttt{k} to the two sub-lists. \texttt{disj*} takes a non-empty list of goals 
% \texttt{gs} and returns a goal. With the help of \texttt{split}, it essentially 
% constructs a \emph{balanced} binary tree where leaves are elements of 
% \texttt{gs} and nodes are \texttt{disj2}s, hence the name of this search 
% strategy.

>>>>

@@

\NOTE[LKC]{submission deadline: Mon 27 May 2019}

@@

\begin{figure}
	\lstinputlisting{Figures/DFSi-0.rkt}
	\caption{implementation of \DFSi{} (Part I)}
	\label{DFSi-0}
\end{figure}

\begin{figure}
	\lstinputlisting{Figures/DFSi-1.rkt}
	\caption{implementation of \DFSi{} (Part II)}
	\label{DFSi-1}
\end{figure}

Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} shows parts that are later compared 
with other search 
strategies. We follow some conventions to name variables: variables bound to 
states are named \texttt{s}; variables bound to goals are named \texttt{g} 
(possibly with subscript); variables bound to search spaces have names ending 
with $^\infty$. Fig.~\ref{DFSi-0} shows the implementation of disjunction. The 
first function, \texttt{disj2}, implements binary disjunction. It applies the 
two disjunctive goals to the input state \texttt{s} and composes the two 
resulting search spaces with \texttt{append$^\infty$}. The following syntax 
definitions say disjunctive operator is right-associative. Fig.~\ref{DFSi-1} 
shows the implementation of conjunction. The first function, \texttt{conj2}, 
implements binary conjunction. 
It applies the \emph{first} goal to the input state, then applies the second 
goal to states in the resulting search space. The latter process is done with a 
helper function. \texttt{append-map$^\infty$} applies its input goal to states 
in its input search spaces and compose the resulting search spaces. It reuses 
\texttt{append$^\infty$} for search space composition. The following syntax 
definitions say conjunctive operator is also right-associative.

@@

Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
\conj{}. The implementation of DFS$_\textrm{bi}$ differs from 
DFS$_\textrm{i}$'s in the \disj{} macro. We list the new \disj{} with its 
helper in Fig.~\ref{balanced-disj}. When there are one or more disjunctive 
goals, \disj{} builds a balanced binary tree whose leaves are the goals and 
whose nodes are \texttt{disj2}s, hence the name of this search strategy. 
The new helper, \texttt{disj+}, takes two additional `arguments'. They 
accumulate goals to be put in the left and right subtrees. The first clause 
handles the case where there is only one goal. In this case, the tree is the 
goal itself. When there are more goals, we partition the list of goals 
into two sublists of roughly equal lengths and recur on the two sublists. Goals 
are moved to the accumulators in the fourth and last clause. As we are moving 
two goals each time, there are two base cases: (1) no goal remains; (2) one 
goal remains. These two base cases are handled in the second clause and the 
third clause respectively. In contrast, the \disj{} in \DFSi{} constructs the 
binary tree in a particularly unbalanced form.
